Integer Programming with Quantum Annealing from an Open Quantum System

### 2021-02-04 paper/v2/main.tex
rewrote integer programming paragraph

\documentclass[prd,twocolumn,tightenlines,preprintnumbers,showpacs,superscriptaddress,notitlepage,nofootinbib,eqsecnum,floatfix,longbibliography,aps,10pt]{revtex4-1}
\pdfoutput=1
\usepackage{CJK}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{amsmath}
\usepackage{mathtools}
\usepackage{amsfonts,dsfont}
\usepackage{bm,bbm}
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage{enumitem}

\usepackage{hyperref}
\hypersetup{
    colorlinks=true,     % false: boxed links; true: colored links
    linkcolor=blue,      % color of internal links
    citecolor=blue,      % color of links to bibliography
    filecolor=blue,      % color of file links
    urlcolor=blue        % color of external links
}

@@

In general, ILP is classically NP-complete, and as a result, heuristic methods are employed~\cite{GLOVER1986533, doi:10.1287/ijoc.1.3.190, doi:10.1287/ijoc.2.1.4}.
Standard classical heuristic algorithms follow a greedy scheme which iteratively approximates optimal solutions--starting from a random initial guess, these algorithms apply locally optimal choices at each step.
The NP-hardness of ILP can be understood by realizing that while the solution to an $n$-dimensional linear problem must lie on the vertices of the feasibility region, while the optimal integer solution may in general be at any integer solution inside the feasibility region.
While greedy algorithms do not guarantee optimal global solutions, they find feasible solutions in polynomial time, which can be utilized in further computations. ILP is a commonly tackled problem applicable to situations such as scheduling, network optimization, and graph optimization such as the minimum dominating set problem (MDS). ILP can also be used to identify reaction pathways of biological system, and has recently been explored in the context of quantum annealing~\cite{2020arXiv200713788H}.

An important ILP application is the MDS problem, which is representatively considered in this work.
For a given a graph $G(E,V)$, defined by the set of $V$ vertices and $E$ edges, a dominating set $D$ is a specific subset of vertices $D \subseteq V$.
In particular, $D$ is a dominating set if all vertices in $V$ but not in $D$ are adjacent to at least one vertex in $D$.
This is equivalent to requiring the set of nearest-neighbor vertices of $D$ (exclusive) and $D$ cover all vertices $N(D) \cup D = V$ (an example is given by Fig.~\ref{fig:dominating_sets}a).
The set $D$ is a minimal dominating set if there is no proper subset of $D$ that is a dominating set, {\it{i.e.}}, the removal of any vertex in $D$ results in $N(D) \cup D  \neq V$.
An example is given by Fig.~\ref{fig:dominating_sets}b.
The domination number of $D$ is given by the cardinality of $|D| \equiv \overline{\overline{D}}$.
The MDS is defined by $D$ with the smallest domination number.
Fig.~\ref{fig:dominating_sets}c shows an example of the MDS of $G(V, E)$ and is different from the minimal dominating set.
We emphasize that while the maximum independent set is always a minimal dominating set as exemplified by Fig.~\ref{fig:dominating_sets}b, the MDS, in general, can have a smaller domination number.
As a result, the solution to the dominating set problem can not be obtained by solving the maximum independent set problem, a well-studied problem for quantum annealers.

>>>>

\documentclass[prd,twocolumn,tightenlines,preprintnumbers,showpacs,superscriptaddress,notitlepage,nofootinbib,eqsecnum,floatfix,longbibliography,aps,10pt]{revtex4-1}
\pdfoutput=1
\usepackage{CJK}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{amsmath}
\usepackage{mathtools}
\usepackage{amsfonts,dsfont}
\usepackage{bm,bbm}
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage{enumitem}
\usepackage{soul}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,     % false: boxed links; true: colored links
    linkcolor=blue,      % color of internal links
    citecolor=blue,      % color of links to bibliography
    filecolor=blue,      % color of file links
    urlcolor=blue        % color of external links
}

@@

While ILP is NP-Hard, extremely large instances of ILP are solved are rutinely solved on a daily basis in a variety of industries such as transportation, energy, and online dating. The fact that instances with millions of integer variables can be solved is due to the incredible improvement in classical ILP methods. One estimate has that the speed of ILP algorithms, combined with hardware improvements, have lead to a speedup of around 200 billion\cite{bertsimas2014statistics}. Despite this fact, there are still very small problems that still require several months, or even years of computational effort to solve. For example, the Steiner Triple Covering problems can be notoriously difficult, an instance with only 135 binary variables, \mathtt{STS135}, required over 120 days of computations~\cite{ostrowski2011solving}. Another example is the football pool problem, where an instance with only 729 binary variables still remains unsolved after years of computational effort~\cite{linderoth2009improving}. In both these cases, the underlying problem is a covering problem.

{\color{red} In general, ILP is classically NP-hard, and as a result, heuristic methods are employed~\cite{GLOVER1986533, doi:10.1287/ijoc.1.3.190, doi:10.1287/ijoc.2.1.4}.
Standard classical heuristic algorithms follow a greedy scheme which iteratively approximates optimal solutions--starting from a random initial guess, these algorithms apply locally optimal choices at each step.
The NP-hardness of ILP can be understood by realizing that while the solution to an $n$-dimensional linear problem must lie on the vertices of the feasibility region, while the optimal integer solution may in general be at any integer solution inside the feasibility region.
While greedy algorithms do not guarantee optimal global solutions, they find feasible solutions in polynomial time, which can be utilized in further computations. ILP is a commonly tackled problem applicable to situations such as scheduling, network optimization, and graph optimization such as the minimum dominating set problem (MDS). ILP can also be used to identify reaction pathways of biological system, and has recently been explored in the context of quantum annealing~\cite{2020arXiv200713788H}.}

In this paper we will consider instances of the minimum dominating set (MDS) problem.  For a given a graph $G(E,V)$, defined by the set of $V$ vertices and $E$ edges, a dominating set $D$ is a specific subset of vertices $D \subseteq V$.
In particular, $D$ is a dominating set if all vertices in $V$ but not in $D$ are adjacent to at least one vertex in $D$.
This is equivalent to requiring the set of nearest-neighbor vertices of $D$ (exclusive) and $D$ cover all vertices $N(D) \cup D = V$ (an example is given by Fig.~\ref{fig:dominating_sets}a).
The set $D$ is a minimal dominating set if there is no proper subset of $D$ that is a dominating set, {\it{i.e.}}, the removal of any vertex in $D$ results in $N(D) \cup D  \neq V$.
An example is given by Fig.~\ref{fig:dominating_sets}b.
The domination number of $D$ is given by the cardinality of $|D| \equiv \overline{\overline{D}}$.
The MDS is defined by $D$ with the smallest domination number.
Fig.~\ref{fig:dominating_sets}c shows an example of the MDS of $G(V, E)$ and is different from the minimal dominating set.
We emphasize that while the maximum independent set is always a minimal dominating set as exemplified by Fig.~\ref{fig:dominating_sets}b, the MDS, in general, can have a smaller domination number.
As a result, the solution to the dominating set problem can not be obtained by solving the maximum independent set problem, a well-studied problem for quantum annealers.
